Meta-analysis

### 2019-07-24 05_MetaAnalysis.Rmd
APPS abstract

### Host genotypes
Host genotype may have to be analysed to determine the effect.  
```{r Host_genotype}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>% 
   group_by(host_genotype) %>%
   summarise(n = length(host_genotype))

>>>>

### Host genotypes
Host genotype may have to be analysed to determine the effect.  
```{r Host_genotype}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>% 
   group_by(host_genotype, Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()

PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   group_by(row_spacing,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()
